### 2023-04-03 application.tex
details

\subsection{VASS, 2-VASS, semilinear VASS, Lossy Channel Systems, Integer et Continuous VASS, Regular Channel Systems}

\begin{theorem}{}
Resilience is decidable for semilinear VASS, LCM, Integer et Continuous VASS when $\Safe$ and $\Bad$ are semilinear sets.
\end{theorem}

se déduit du papier Schnoebelen RP 2010, page 8

@@

We may consider context-free grammars.

\begin{corollary}
{\sc resilience} is decidable for finite automata and context-free grammars (seen as transition systems)
\end{corollary}

\begin{proof}

  \textcolor{red}{à faire Mathieu}
Context-free grammars are WSTS \cite{DBLP:journals/tcs/FinkelS01} \alain{monotony ne semble pas strong...}avec $\uparrow post^*$ calculable (because the reachability set of a pushdown machine is an effectively computable regular language) ???? resilience decidable.
\end{proof}

@@

\subsection{Timed Automata}

@@

>>>>

\subsection{Pushdown automata}

%We may consider context-free grammars.

\begin{corollary}
{\sc resilience} is decidable for pushdown automata.
\end{corollary}

\begin{proof}
pushdown automata $\uparrow post^*$ calculable (because the reachability set of a pushdown machine is an effectively computable regular language) ???? resilience decidable.

  \textcolor{red}{à faire Mathieu}
Context-free grammars are WSTS \cite{DBLP:journals/tcs/FinkelS01} \alain{monotony ne semble pas strong...}avec $\uparrow post^*$ calculable (because the reachability set of a pushdown machine is an effectively computable regular language) ???? resilience decidable.
\end{proof}
%
%
\subsection{LCM, VASS, semilinear VASS, Integer et Continuous VASS}

\begin{theorem}{}
Resilience is decidable for LCM, semilinear VASS, Integer et Continuous VASS when $\Safe$ and $\Bad$ are semilinear sets.
\end{theorem}

se déduit du papier Schnoebelen RP 2010, page 8. RP is decidable for lossy counter machines (LCM) with $\Safe$ and $\Bad$ semilinear sets as a consequence of results in Section 3.4 of \cite{DBLP:conf/rp/Schnoebelen10}.

@@

@@

\subsection{Regular Channel Systems}

corollary: Lossy Channel Systems.

%
\iffalse
%
\subsection{Timed Automata}

@@

%
\fi
%

### 2023-04-03 resilience.tex
details

In \cite{DBLP:conf/gg/Ozkan22}, the authors considered that $\Bad$ is downward closed and $\Safe$ is upward closed.
%		
RP is decidable for lossy counter machines (LCM) with $\Safe$ and $\Bad$ semilinear sets as a consequence of results in Section 3.4 of \cite{DBLP:conf/rp/Schnoebelen10}. We deduce 
% \textcolor{red}{that the three resilience problems are decidable for all four pairs of sets $\Safe$ and $\Bad$ downward closed and upward closed sets.}
% \mathieu{changer ça}
decidability results for the four pairs of sets $\Safe$ and $\Bad$ downward closed and upward closed as seen in Section~\ref{synthesis}.

@@

{\bf Synthesis}\label{synthesis}

>>>>

Surprinsingly, the decidability of resilience problems was not studied in the previous papers.

In \cite{DBLP:conf/gg/Ozkan22}, the authors considered that $\Bad$ is downward closed and $\Safe$ is upward closed.
%		
We deduce 
% \textcolor{red}{that the three resilience problems are decidable for all four pairs of sets $\Safe$ and $\Bad$ downward closed and upward closed sets.}
% \mathieu{changer ça}
decidability results for the four pairs of sets $\Safe$ and $\Bad$ downward closed and upward closed as seen in Section~\ref{synthesis}.

@@

{\bf Synthesis of the main results}\label{synthesis}
